---
title: "Weight of Fish"
author: "Estefania Maldonado"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <-filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ .,
                           data = Perch,
                           nbest = 1,
                           nvmax = NULL,
                           force.in = NULL, force.out = NULL,
                           method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

```{r}
library(car)
subsets(regsubsets.out, statistic="adjr2", legend = "bottom", main ="adjr2")
```


### Best Models

The best model is the two element model; H & W models.

### Best Two regressor model

The best two regressive model is also the model H & W.

## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ .,
                           data = Pike,
                           nbest = 1,
                           nvmax = NULL,
                           force.in = NULL, force.out = NULL,
                           method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2", legend = "bottom", main ="adjr2")
```

### Best Models

The best model is model5, corresponding to L1-L2-L3-H-W.

### Best Two regressor model

The best two regressor model is model2; L1-L3.

The best model is different to the best two regressor model so we will run ANOVA.

```{r}
model5=lm(Weight~ . ,data=Pike)
summary.lm(model5)
model2=lm(Weight~ . -Length2-Height-Width , data=Pike)
model3=lm(Weight~ . -Length2-Height , data=Pike)
anova(model5,model2)
```


## Roach

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ .,
                           data = Roach,
                           nbest = 1,
                           nvmax = NULL,
                           force.in = NULL, force.out = NULL,
                           method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2", legend = "bottomleft", main ="adjr2")
```

### Best Models
Seems like the best model is model 2, where we can find L3 and W.

### Best Two regressor model

The best model and the best regressor model are both the same, being model 2= L3-W.

## Final Summary Statements
For Perch and Roach the best models and the best two regressor models are the same; the model 2 for both of them so we didn't have to compare or use ANOVA to find the p-value. On the other hand, Pike had a different best model; model5, corresponding to L1-L2-L3-H-W and for the best two regressor model is model2; L1-L3.For instance, we ran ANOVA using these two models to determine the p-value which was 8.679e-10.

